Combining neural networks and geostatistics for landslide hazard assessment of San Salvador Department, El Salvador \newline \newline Combinando redes neuronales y geoestadística para evaluación de deslizamientos de tierra en San Salvador,Departamento de El Salvador

### 2015-05-25 paper.tex

@@

>>>>

There are two important applications of the neural network models to landslide susceptibility. The first (\cite{Yesilnacar2005251})

@@

\bibitem{Yesilnacar2005251}
E. Yesilnacar and T. Topal.
\newblock Landslide susceptibility mapping: A comparison of logistic regression and neural networks methods in a medium scale study, Hendek region (Turkey).
\newblock \emph{Engineering Geology}, 79\penalty0
  (11):\penalty0 251-266, 2005.
\newblock ISSN 0013-7952,
%\newblock \doi{10.1080/01431160310001618734}.
\newblock URL
  \url{http://www.sciencedirect.com/science/article/pii/S0013795205000384}.
